Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-08-07 paper/ms.tex
Updated footnote 5.

The original \MESA\ model was in equilibrium, but to ensure
the uniformly-gridded model was in hydrostatic equilibrium we
constructed the appropriate pressure profile. This was done by
integrating for the pressure in each zone from the central point up,
accounting for the local acceleration of gravity, temperature,
composition, and the mass below and enclosed by the zone. As
with \citet{willcoxetal2016}, we used the EOS routine from
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
Helmholtz EOS table used in \CASTRO\ is in the public BoxLib
Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} 
This procedure produced a structure that was stable in \FLASH, with 
fluctuations in central density less than $3\%$, for at least $5$ 
seconds with no energy deposition.

>>>>

The original \MESA\ model was in equilibrium, but to ensure
the uniformly-gridded model was in hydrostatic equilibrium we
constructed the appropriate pressure profile. This was done by
integrating for the pressure in each zone from the central point up,
accounting for the local acceleration of gravity, temperature,
composition, and the mass below and enclosed by the zone. As
with \citet{willcoxetal2016}, we used the EOS routine from
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} 
This procedure produced a structure that was stable in \FLASH, with 
fluctuations in central density less than $3\%$, for at least $5$ 
seconds with no energy deposition.
